100 years of Pies vs. Bars

### 2024-11-25 index.qmd
title change

---
title: "Enhancing Data Visualization: Insights from Graphical Perception and Comparative Analysis of Charts"
format:
  pdf:
    keep-tex: true
    documentclass: article
    papersize: letter
    fontsize: 10pt
    template-partials:
      - title.tex
      - before-bib.tex
    include-in-header:
      - text: |
          \usepackage{sdss2020} % Uses Times Roman font (either newtx or times package)
          \usepackage{url}
          \usepackage{hyperref}
          \usepackage{latexsym}
          \usepackage{amsmath, amsthm, amsfonts}
          \usepackage{algorithm, algorithmic}
          \usepackage[dvipsnames]{xcolor} % colors
          \newcommand{\mt}[1]{{\textcolor{blue}{#1}}}
          \newcommand{\svp}[1]{{\textcolor{RedOrange}{#1}}}
    classoption: [twocolumn]
    mainfont: Times New Roman
    colorlinks: true
author:
  - name: Maksuda Atkar Toma
    affiliation:
      department: Statistics Department
      name: University of Nebraska, Lincoln
    email: mtoma2@huskers.unl.edu
    corresponding: true
  - name: Susan Vanderplas
    affiliation:
      department: Statistics Department
      name: University of Nebraska, Lincoln
    email: svanderplas2@unl.edu
    orcid: 0000-0002-3803-0972
bibliographystyle: acl
bibliography: refs.bib
filters:
   - latex-environment
commands: [mt,svp]
---

>>>>

---
title: "100 years of Pies vs. Bars"
format:
  pdf:
    keep-tex: true
    documentclass: article
    papersize: letter
    fontsize: 10pt
    template-partials:
      - title.tex
      - before-bib.tex
    include-in-header:
      - text: |
          \usepackage{sdss2020} % Uses Times Roman font (either newtx or times package)
          \usepackage{url}
          \usepackage{hyperref}
          \usepackage{latexsym}
          \usepackage{amsmath, amsthm, amsfonts}
          \usepackage{algorithm, algorithmic}
          \usepackage[dvipsnames]{xcolor} % colors
          \newcommand{\mt}[1]{{\textcolor{blue}{#1}}}
          \newcommand{\svp}[1]{{\textcolor{RedOrange}{#1}}}
    classoption: [twocolumn]
    mainfont: Times New Roman
    colorlinks: true
author:
  - name: Maksuda Atkar Toma
    affiliation:
      department: Statistics Department
      name: University of Nebraska, Lincoln
    email: mtoma2@huskers.unl.edu
    corresponding: true
  - name: Susan Vanderplas
    affiliation:
      department: Statistics Department
      name: University of Nebraska, Lincoln
    email: svanderplas2@unl.edu
    orcid: 0000-0002-3803-0972
bibliographystyle: acl
bibliography: refs.bib
filters:
   - latex-environment
commands: [mt,svp]
---
